### 2024-08-16 paper.tex
get started

\section{Simplifying the definition of a Springer fiber at a Slodowy slice}
\par Let \(\mathcal{N}_m \subseteq \gl_m(\mathbb{C})\) be the subset consisting of nilpotent elements.
For \(X \in \mathcal{N}_m\) and \(a, b \in \mathbb{C}^m\), let
\[A_{X, a, b} = \begin{pNiceArray}{ccc|ccccc}
 & & & & & & & \vert \\
 & X & & & & & & b    \\
 & & & & & & & \vert \\
\hline
\text{---} & a & \text{---} & 0 \\
& & & 1 & 0 \\
& & &  & 1 & \ddots \\
& & &  &   & \ddots & 0 \\
& & &  &   &  & 1 & 0
\end{pNiceArray} \in \mathfrak{gl}_{m + n}(\mathbb{C}).\]
By the definition given in the previous section, we have 
\[\widetilde{\mathcal{N}}_{m, n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}',\]
and the Springer fiber at the \(n\)-Slodowy slice at a nilpotent \(X \in \gl_m\) is
\[\pi_{m,n}^{-1}(X) = \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \in \mathcal{S}_{m, n}'\} \] 
\[= \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{nilpotent}\}\]
\[\cong \{(\mathfrak{b}, a, b) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{ nilpotent}\}.\]
We will make one last simplification to this by using a correspondence between Borel subalgebras and complete flags.
TODO: fix the next few paragraphs, they are out of context.
\par We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
Since \(H\) is the set of \(X\) which preserve \(E\),
\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
So, for \(X \in \mathcal{N}\),
\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\}.\]
\par In this section we will find the irreducible components of \(\pi^{-1}(X)\).
Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
\par Let \(\lambda\) be the shape of \(X\), and let \((e_{ij})_{i \leq r, j \leq \lambda_i}\) be a Jordan basis for \(X\), with \(X e_{ij} = e_{i,j - 1}\).
Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).

>>>>

\section{Simplifying the definition of a Springer fiber at a Slodowy slice}
\par Let \(\mathcal{N}_m \subseteq \gl_m(\mathbb{C})\) be the subset consisting of nilpotent elements.
For \(X \in \mathcal{N}_m\) and \(a, b \in \mathbb{C}^m\), let
\[A_{X, a, b} = \begin{pNiceArray}{ccc|ccccc}
 & & & & & & & \vert \\
 & X & & & & & & b    \\
 & & & & & & & \vert \\
\hline
\text{---} & a & \text{---} & 0 \\
& & & 1 & 0 \\
& & &  & 1 & \ddots \\
& & &  &   & \ddots & 0 \\
& & &  &   &  & 1 & 0
\end{pNiceArray} \in \mathfrak{gl}_{m + n}(\mathbb{C}).\]
By the definition given in the previous section, we have 
\[\widetilde{\mathcal{N}}_{m, n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}',\]
and the Springer fiber at the \(n\)-Slodowy slice at a nilpotent \(X \in \gl_m\) is
\[\pi_{m,n}^{-1}(X) = \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \in \mathcal{S}_{m, n}'\} \] 
\[= \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{nilpotent}\}\]
\[\cong \{(\mathfrak{b}, a, b) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{ nilpotent}\}.\]
We will make one last simplification to this by using a correspondence between Borel subalgebras and complete flags.
TODO: fix the next few paragraphs, they are out of context.
\par We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
Since \(H\) is the set of \(X\) which preserve \(E\),
\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
So, for \(X \in \mathcal{N}\),
\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]

\section{Finding the Springer fiber at a Slodowy slice}
\par Fix any \(X \in \mathcal{N}\).
In this section we find the irreducible components of
\[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]

\begin{lemma}
    \(V = V_0 \cup \bigcup_{w, r} V_{w,r}\), where 
    \[V_0 = \{(U, 0, b)\} \subseteq V,\]
    and
    \[V_{w,r} = \{(U, a, b) : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \} \subseteq V.\]
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, we will find the irreducible components of \(V_0\) and the \(V_{w,r}\).
These will all happen to be equidimensional, so we will see that their closures in \(V\) are the irreducible components of \(V\).
\par We begin with \(V_0\), which will be easy.

% Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).
